ms_figures

### 2023-02-07 ms_figures.Rmd
updated ms figures

library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)
library(tidytext)
library(cowplot)
```

@@

```{r fig1, fig.height = 12, fig.width = 7.5}
ggarrange(fig1a,
          ggarrange(fig1b,
                    fig1c_out_degree,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("b", "c")),
          ggarrange(fig1d,
                    fig1e,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("d", "e")),
          common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 3, labels = c("a", ""))

@@

```{r fig2, fig.height=8, fig.width=7}
# Overall Figure 2
ggarrange(ggarrange(fig2a, NULL,
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 0.2), labels = c("a", "")), 
          fig2b, labels = c("", "b"),
          ncol = 1, heights = c(1.75, 4))

@@

```{r fig3, fig.height = 6, weight = 8}
fig3 <- ggarrange(
  ggarrange(fig3a, fig3b, 
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("a", "b")),
  ggarrange(fig3c, fig3d,
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("c", "d")),
  nrow = 2
)

@@

```{r fig4a}
fig4a_data <- read.csv(file.path(datadir, "fig4a_data.csv"))

@@

@@

```{r fig4b}
# NOTE: Rahul - we need to have the correct file read in here. For reference, the file currently generating this and the new fig 4d is "/Volumes/jgephart/ARTIS/Outputs/diversity/max_per_capita_100kg/diversity.csv"
# I am not sure we should go with these colors, but didn't have time to keep messing with this
# These comments also apply to the new fig4c

fig4b <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Production" = "shannon_prod", "Imports" = "shannon_imports", "Exports" = "shannon_exports") %>% 
  pivot_longer(Production:Exports, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Production", "Imports", "Exports"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[1], habitat_source_colors[3], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())

```{r fig4c}
fig4c <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Domestic" = "shannon_domestic", "Foreign" = "shannon_foreign") %>% 
  pivot_longer(Domestic:Foreign, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Domestic", "Foreign"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[2], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())

@@

```{r fig4c_old}
fig4c_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4c <- fig4c_data %>%
  ggplot(aes(x = imports/1000000, y = shannon_supply, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10() +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total imports (million t, live weight)",
       y = "Supply diversity",
       color = "")

```{r fig4, fig.height = 8, fig.width = 12}
fig4 <- ggarrange(fig4a, 
          ggarrange(fig4b,
                    fig4c,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("b", "c")),
          nrow = 2,
          labels = c("a", "", "")
          )

@@

exporters_old_plot <- top_exporters_old %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(exporter_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

ggarrange(
  exporters_old_plot,
  exporters_recent_plot,
  ncol = 2,
  labels = c("Old", "Recent")
)

>>>>

library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)
library(tidytext)
library(cowplot)
library(scales)
```

@@

```{r fig1, fig.height = 7, fig.width = 5}
ggarrange(fig1a,
          ggarrange(fig1b,
                    fig1c_out_degree,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("b", "c")),
          ggarrange(fig1d,
                    fig1e,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("d", "e")),
          common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 3, labels = c("a", ""))

@@

```{r fig2, fig.height=4, fig.width=3}
# Overall Figure 2
ggarrange(ggarrange(fig2a, NULL,
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 0.2), labels = c("a", "")), 
          fig2b, labels = c("", "b"),
          ncol = 1, heights = c(1.75, 4))

@@

```{r fig3, fig.height = 4, fig.width = 5}
fig3 <- ggarrange(
  ggarrange(fig3a, fig3b, 
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("a", "b")),
  ggarrange(fig3c, fig3d,
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("c", "d")),
  nrow = 2
)

@@

```{r fig4a_old, eval = FALSE}
fig4a_data <- read.csv(file.path(datadir, "fig4a_data.csv"))

@@

```{r fig4a}
diversity <- read.csv("/Volumes/jgephart/ARTIS/Outputs/diversity/max_per_capita_100kg/diversity.csv")
fig4a <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Production" = "shannon_prod", "Imports" = "shannon_imports", "Exports" = "shannon_exports") %>% 
  pivot_longer(Production:Exports, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Production", "Imports", "Exports"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[1], habitat_source_colors[3], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())

@@

```{r fig4b}
fig4b <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Domestic" = "shannon_domestic", "Foreign" = "shannon_foreign") %>% 
  pivot_longer(Domestic:Foreign, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Domestic", "Foreign"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[2], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())

@@

```{r fig4d}
fig4d_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4d <- fig4d_data %>%
  # total supply greater than 1 tonne (FIXIT update manuscript caption)
  filter(supply > 1) %>%
  ggplot(aes(x = imports/1000000, y = shannon_supply, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "b") +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total imports (million t, live weight)",
       y = "Supply diversity",
       color = "")

#

fig4d
```
```{r fig4e}
fig4e_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4e <- fig4e_data %>%
  # total supply greater than 1 tonne (FIXIT update manuscript caption)
  filter(supply > 1) %>%
  ggplot(aes(x = exports/1000000, y = shannon_supply, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "b") +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total exports (million t, live weight)",
       y = "Supply diversity",
       color = "")

#

fig4e
```

```{r fig4, fig.height = 7, fig.width = 7}
fig4 <- ggarrange(fig4a,
                  fig4b,
          ggarrange(fig4d,
                    fig4e,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("c", "d")),
          nrow = 3,
          labels = c("a", "b", "")
          )

@@

exporters_old_plot <- top_exporters_old %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(exporter_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  xlim(c(0,6)) +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

@@

ggarrange(
  exporters_old_plot,
  exporters_recent_plot,
  ncol = 2,
  labels = c("'96-'00", "'16-'20")
)
